Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-20 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response/prl_reply/supplemental/supp.tex
updated PRL/supp/reply

\includegraphics[scale=0.24]{plots/Em_and_Q2_CUT_80MeV_35deg.png}

@@

\includegraphics[scale=0.24]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}

@@

\includegraphics[scale=0.22]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}

@@

\includegraphics[scale=0.22]{plots/collimator_CUT_80MeV_35deg_data.png}

@@

  projected at the SHMS collimator.}

@@

\includegraphics[scale=0.24]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.}

@@

  a 40 MeV range, each. (right) The SHMS $z$-reaction vertex corresponding to the specified region in the missing energy spectrum. Inset (left): Missing energy spectrum on a logarithmic
  scale.}

@@

\section{\large Systematic Uncertainty Studies on Event Selection Cuts, Radiative and Bin-Centering Corrections }
\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
\begin{subequations}
  \begin{align}
    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
  \end{align}
\end{subequations}
where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
error accounts for the possible correlation between the two measurements. By taking the ratio
\begin{equation}
  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
\end{equation}
a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error. For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible. Similar plots for the other event selection
cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
\includegraphics[scale=0.4]{plots/Em_syst.png}
\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
\label{fig:Em_sys}
\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated
using the Barlow ratio approach described above. In this case, the ratio was calculated from the difference between the experimental cross

@@

%\clearpage
\bibliography{supp}

>>>>

\includegraphics[scale=0.33]{plots/Em_and_Q2_CUT_80MeV_35deg.png}

@@

\includegraphics[scale=0.33]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}

@@

\includegraphics[scale=0.33]{plots/coin_and_eCal_CUT_80MeV_35deg.png}
\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeter normalized by the particle track momentum (right).}

@@

\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_data.png}

@@

  projected at the SHMS collimator. The $z$-axis (color palette) is in arbitrary units.}

@@

\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.  The $z$-axis (color palette) is in arbitrary units.}

@@

  a 40 MeV range, each.  Inset (left): Missing energy spectrum on a logarithmic scale. (right) The SHMS $z$-reaction vertex corresponding to
  the specified region in the missing energy spectrum.}

@@

\section{\large Systematic Uncertainty Studies on Radiative and Bin-Centering Corrections }
%\indent A study of the sensitivity on the experimental cross section due to variations in the event selection cuts was carried out. 
%To determine if the variation in each of the cuts contributes to a systematic effect and whether this contribution is significant
%enough to be considered as a systematic error, we used the approach by R. Barlow described in Ref. \cite{barlow2002systematic}.\\
%\indent Consider a cross section measurement done two different ways (i.e., apply different cuts). Let the measurements and their
%statistical uncertainties be: ($\sigma^{\mathrm{exp}}_{\mathrm{1}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{1}}$) and ($\sigma^{\mathrm{exp}}_{\mathrm{2}}\pm\delta\sigma^{\mathrm{exp}}_{\mathrm{2}}$)
%where one of the measurements is a subset of the other. The difference and its associated uncertainty can be expressed as,
%\begin{subequations}
%  \begin{align}
%    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
%    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},
%  \end{align}
%\end{subequations}
%where the error of the difference between the two measurements is found by taking the difference of their variance. As demonstrated in Ref.\cite{barlow2002systematic}, this
%error accounts for the possible correlation between the two measurements. By taking the ratio
%\begin{equation}
%  R_{\mathrm{Barlow}} \equiv \frac{\Delta}{\sigma_{\Delta}},
%\end{equation}
%a criterion imposed on $R_{\mathrm{Barlow}}$ determines whether the difference is significant enough to be considered as a systematic error or sufficiently small that it may be
%ignored. This criterion requires knowledge of the correlation between the subsets, but in general, as suggested in Ref.\cite{barlow2017}: if $R_{\mathrm{Barlow}} < 2$ (or $\Delta <2\sigma_{\Delta}$)
%the test passes and if $R_{\mathrm{Barlow}} > 4$ (or $\Delta >4\sigma_{\Delta}$), the test fails and the discrepancy must be added as a systematic error. For $2<R_{\mathrm{Barlow}}<4$, a judgement must be made.\\
%\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
%In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,
%the Barlow ratio was kept within 2-4 standard deviations with the exception of a few outliers which can be understood from the fact that these might have very similar variances. These systematic
%studies were mainly done to check the stability of the event selection cuts and the effects of cut variation on the cross section were found to be negligible. Similar plots for the other event selection
%cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 
%\clearpage
%\begin{figure}[!ht]
%\includegraphics[scale=0.4]{plots/Em_syst.png}
%\caption{Systematic effects of the missing energy cut on the data cross section for $\theta_{nq}=35^{\circ}$ (left) and $45^{\circ}$ (right). The inner (black dashed) and outer (black solid)
%  lines represent the $\Delta=\pm2\sigma_{\Delta}$ and $\pm4\sigma_{\Delta}$ boundaries, respectively.}
%\label{fig:Em_sys}
%\end{figure}
\indent The systematic effect on the cross sections due to model dependency of the radiative and bin-centering corrections was investigated (see Section 5.10 of Ref. \cite{cyero_phdthesis})
using the Barlow ratio approach \cite{barlow2002systematic,barlow2017}. In this case, the ratio was calculated from the difference between the experimental cross

@@

\indent Systematic studies of the event selection cuts described above were also carried out using the R. Barlow approach. The studies demonstrated that variations in the software had a negligible
effect in the measured cross sections and thus no systematic uncertainties due to software cuts were included in the final result. For a detailed discussion of these studies see Section 5.10 of Ref. \cite{cyero_phdthesis}.
\\\\
\bibliography{supp}
